\documentclass[twocolumn,linenumbers]{aastex62}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand\addcitation{{\color{red}[CITATION]}}

\usepackage{amsmath}
\usepackage{cancel}
\usepackage{float}

\shorttitle{Updated Opacities for DSEP}
\shortauthors{Boudreaux et al.}
% \watermark{DRAFT}
% \graphicspath{{./}{figures/}{src/figures}}

\begin{document}

\title{Correlations between Ca II H\&K Emission and the Gaia M dwarf Gap}

\correspondingauthor{Emily M. Boudreaux}
\email{emily.m.boudreaux.gr@dartmouth.edu,\\emily@boudreauxmail.com}

\author[0000-0002-2600-7513]{Emily M. Boudreaux}
\affiliation{Department of Physics and Astronomy, Dartmouth College, Hanover, NH 03755, USA}

\author[0000-0001-9828-3229]{Aylin Garcia Soto}
\affiliation{Department of Physics and Astronomy, Dartmouth College, Hanover, NH 03755, USA}

\author[0000-0003-3096-4161]{Brian C. Chaboyer}
\affiliation{Department of Physics and Astronomy, Dartmouth College, Hanover, NH 03755, USA}

\received{02/07/2024}
\revised{02/20/2024}
\accepted{}
\submitjournal{ApJ}


\begin{abstract}
  The Gaia M dwarf gap, also known as the Jao Gap, is a novel feature
  discovered in the Gaia DR2 G vs. BP-RP color magnitude diagram. This gap
  represents a 17 percent decrease in stellar density in a thin magnitude band
  around the convective transition mass ($\sim 0.35 M_{\odot}$) on the main
  sequence. Previous work has demonstrated a paucity of Hydrogen Alpha emission
  coincident with the G magnitude of the Jao Gap in the solar neighborhood. The
  exact mechanism which results in this paucity is as of yet unknown; however,
  the authors of the originating paper suggest that it may be the result of
  complex variations to a star's magnetic topology driven by the Jao Gap's
  characteristic formation and breakdown of stars' radiative transition zones.
  We present a follow up investigating another widely used magnetic activity
  metric, Calcium II H\&K emission. Ca II H\&K activity appears to share a
  similar anomalous behavior as H$\alpha$ does near the Jao Gap magnitude. We
  observe an increase in star-to-star variation of magnetic activity near the
  Jao Gap. \textbf{We present a toy model of a stars magnetic field evolution
  which demonstrates that} this increase may be due to stochastic disruptions
  to the magnetic field originating from the periodic mixing events
  characteristic of the convective kissing instabilities which drive the
  formation of the Jao Gap.
\end{abstract}

\keywords{Stellar Evolution (1599) --- Stellar Evolutionary Models (2046)}

\input{sections/intro.tex}

\input{sections/results.tex}

\input{sections/modeling.tex}

\input{sections/conclusion.tex}



\acknowledgments{
  This work has made use of the NASA astrophysical data system (ADS). We would
  like to thank Elisabeth Newton, Aaron Dotter, and Gregory Feiden for their
  support and for useful discussion related to the topic of this paper.
  Additionally, we would like to thank Keighley Rockcliffe, Kara Fagerstrom,
  and Isabel Halstead for their useful discussion related to this work.
  \textbf{Finally, we would like to thank the referee for their careful reading and
  critique of this article}. We acknowledge the support of a NASA grant (No.
  80NSSC18K0634). 
}
\acknowledgments

% \begin{acknowledgments}
% 	This work has made use of the NASA astrophysical data system (ADS). We
% 	would like to thank Elisabeth Newton, Aaron Dotter, and Gregory Feiden for
% 	their support and for useful discussion related to the topic of this paper.
% 	We would like to thank our reviewer for their critical eye and their
% 	guidance to investigate to effects of the mixing length on the Gap
% 	Location. Additionally, we would like to thank James Colgan and the Los
% 	Alamos T-1 group for their assistance with the OPLIB opacity tables and
% 	support for the public release of \texttt{pyTOPSScrape}. We acknowledge the
% 	support of a NASA grant (No. 80NSSC18K0634). 
% \end{acknowledgments}

\software{
  The Dartmouth Stellar Evolution Program (\texttt{DSEP}) \citep{Dotter2008},
	\texttt{BeautifulSoup} \citep{richardson2007beautiful},
	\texttt{mechanize} \citep{chandra2015python},
	\texttt{FreeEOS} \citep{Irwin2012},
	\texttt{pyTOPSScrape} \citep{Boudreaux22},
  \texttt{lightkurve} \citep{LightkurveCollaborationLightkurve2018},
  \texttt{stella} \citep{FeinsteinStella2020},
  \texttt{starspot} \citep{AngusRuthAngus2021,Angus2023}
}


\bibliography{ms}{}
\bibliographystyle{aasjournal}


\end{document}

